MULTI process challenge : the FML solution

### 2021-03-03 1-Main.tex

%\documentclass[preprint]{acmart}
\documentclass[preprint]{elsarticle}
\journal{Science of Computer Programming}

@@

\lstdefinestyle{mystyle}{
    backgroundcolor=\color{backcolour},   
    commentstyle=\color{codegreen},
    keywordstyle=\color{magenta},
    numberstyle=\tiny\color{codegray},
    stringstyle=\color{codepurple},
    basicstyle=\ttfamily\footnotesize,
    breakatwhitespace=false,         
    breaklines=true,                 
    captionpos=b,                    
    keepspaces=true,                 
    numbers=left,                    
    numbersep=5pt,                  
    showspaces=false,                
    showstringspaces=false,
    showtabs=false,                  
    tabsize=2https://www.overleaf.com/project/5efee0e8ad6bc10001d47854
}

\lstset{style=mystyle}

\DeclareTextFontCommand{\mytexttt}{\ttfamily\hyphenchar\font=45\relax}

@@

\section{Related work}
\label{sec:relatedwork}
\input{9-RelatedWork.tex}

\input{10-Conclusions.tex}

>>>>

%\documentclass[preprint]{acmart}
\documentclass[preprint]{elsarticle}
\journal{EMISA Journal}

@@

@@

\section{Related work}
\label{sec:relatedwork}
\input{9-Relatedworks.tex}

\section{Conclusions}
\input{10-Conclusions.tex}
